---
title: "Summer Flounder Conceptual Model: Risk Factors"
author: "Geret DePiper, Sarah Gaichas, Brandon Muffley"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

PKG <- c(#"foreign","foodweb","sna",
         "DiagrammeR","circlize","RColorBrewer","QPress",
         "chorddiag", "kableExtra", "googledrive", "readxl")

for (p in PKG) {
  if(!require(p,character.only = TRUE)) {
    install.packages(p)
    require(p,character.only = TRUE)}
}

#install QPress
#install.packages(c("tcltk2", "XML", "devtools"))
#devtools::install_github("SWotherspoon/QPress", build_vignettes = TRUE)

#install chorddiag
#devtools::install_github("mattflor/chorddiag")

#install googlesheets4
#devtools::install_github("tidyverse/googlesheets4")

```

## Background

The Mid-Atlantic Fishery Management Council's Ecosystem Approach to Fisheries Management (EAFM) uses ecosystem indicators within a risk assessment framework to identify high-priority issues for further development of potential management actions, as described [here](http://www.mafmc.org/eafm).

>Development of conceptual models to address management questions regarding the highest priority ecosystem factors is the second step in the Council’s EAFM Guidance Document framework. These models are built to ensure that key relationships throughout the system are accounted for. Utilizing the results of the risk assessment, the Council agreed to begin piloting the development of a summer flounder conceptual model that will consider the high priority risk factors affecting summer flounder and its fisheries.

This page provides interactive views of the risk factors mapped in the draft conceptual model for summer flounder developed for the Mid-Atlantic Fishery Management Council by a working group:

```{r grouptab}
# table with group membership

name <- c("Greg Ardini", "Mark Terceiro", "Michael Wilberg",  "Douglas Lipton",  "Kiley Dancy", "Jessica Coakley","Kirby Rootes-Murdy", "Jason McNamee",  "Jeff Brust", "Danielle Palmer",  "Emily Gilbert",  "Robert O'Reilly", "G. Warren Elliott", "Charles Perretti", "Geret DePiper", "Sarah Gaichas", "Brandon Muffley")

affiliation <-c("NEFSC", "NEFSC", "UMD", "NMFS", "MAFMC", "MAFMC", "ASMFC", "RI DEM", "NJ DEP", "GARFO", "GARFO", "EOP & VMRC", "EOP Chair", "NEFSC", "NEFSC", "NEFSC", "MAFMC")
  
subgroup <- c("Human Dimensions", "Physical Environment", "Physical Environment", "Human Dimensions", "Human Dimensions", "Physical Environment", "Human Dimensions", "Physical Environment", "Physical Environment","Human Dimensions","Human Dimensions","Human Dimensions","Human Dimensions","Physical Environment", "Both","Both","Both")

wg <- data.frame(Name=name, Affiliation=affiliation, Subgroup=subgroup)

knitr::kable(wg, caption = "Summer Flounder Conceptual Model Working Group 2019") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```


```{r sfmod setup, message=FALSE}
#assumes this is a project and .dia file is in local directory
edges <- model.dia("Summer_Flounder_July22_2019.dia")

## Examine unweighted adjacency matrix
FLUKE <- adjacency.matrix(edges, labels=TRUE)

FLUKE_Drivers <- c("Economic Drivers","Temperature","Shifts in Preferences","Community Vulnerability","Freshwater Influx","Nutrient Influx","Ocean Acidification",
                   "Ocean Features","Oceanographic Transport","Dissolved Oxygen","Water Diversion")
FLUKE_Habitat <- c("Estuarine Habitat","Food Web Changes","Offshore Habitat","Habitat Alteration","Habitat Disturbance","Loose Inert Substrate","Salinity","Water Clarity",
                   "Aquatic Vegetation")
FLUKE_Biota <- c("Fluke Distributional Shift","Fluke Recruitment","Fluke SSB","Adults & Spawners","Age & Size Structure",
                 "Growth","Maturation","Natural Mortality","Sex Ratio")
FLUKE_Species <- c("Other Species Distributional Shifts","Protected Species")
FLUKE_Management <- c("Allocation","Communication","Enforcement","Management Control","Other Regulations",
                      "Permit Access","Regulatory Complexity","Risk Buffering")
FLUKE_Benefits <- c("Commercial Profits","Consumer Surplus","Recreational Value","Seafood","Recreational Profits")
FLUKE_Science <- c("Assessment Process","Data Quality","Predictability of Recreational Fishing","Stock Assessment")
FLUKE_Fishery <- c("Compliance","Discards","Fishery Distributional Shift","Fishery Resilience",
                   "Fleet Diversity","Landings","Perceived Inequity","Technical Interactions")

FLUKE_C <- brewer.pal(8,"Dark2")

FLUKE_Colors <- data.frame(row.names(FLUKE))
colnames(FLUKE_Colors) <- "Focus"

FLUKE_Colors$Color <- FLUKE_C[1]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Habitat] <- FLUKE_C[2]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Biota] <- FLUKE_C[3]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Species] <- FLUKE_C[4]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Management] <- FLUKE_C[5]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Benefits] <- FLUKE_C[6]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Science] <- FLUKE_C[7]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Fishery] <- FLUKE_C[8]

FLUKE_Groups <- FLUKE_Colors
FLUKE_Groups$Group <- "Drivers"
FLUKE_Groups$Rank <- 1
FLUKE_Groups$Group[FLUKE_Groups$Focus%in%FLUKE_Habitat] <- "Habitat"
FLUKE_Groups$Rank[FLUKE_Groups$Focus%in%FLUKE_Habitat] <- 2
FLUKE_Groups$Group[FLUKE_Groups$Focus%in%FLUKE_Biota] <- "Fluke Dynamics"
FLUKE_Groups$Rank[FLUKE_Groups$Focus%in%FLUKE_Biota] <- 3
FLUKE_Groups$Group[FLUKE_Groups$Focus%in%FLUKE_Species] <- "Other Biota"
FLUKE_Groups$Rank[FLUKE_Groups$Focus%in%FLUKE_Species] <- 4
FLUKE_Groups$Group[FLUKE_Groups$Focus%in%FLUKE_Management] <- "Management"
FLUKE_Groups$Rank[FLUKE_Groups$Focus%in%FLUKE_Management] <- 5
FLUKE_Groups$Group[FLUKE_Groups$Focus%in%FLUKE_Benefits] <- "Benefits"
FLUKE_Groups$Rank[FLUKE_Groups$Focus%in%FLUKE_Benefits] <- 6
FLUKE_Groups$Group[FLUKE_Groups$Focus%in%FLUKE_Science] <- "Science"
FLUKE_Groups$Rank[FLUKE_Groups$Focus%in%FLUKE_Science] <- 7
FLUKE_Groups$Group[FLUKE_Groups$Focus%in%FLUKE_Fishery] <- "Fishing Fleets"
FLUKE_Groups$Rank[FLUKE_Groups$Focus%in%FLUKE_Fishery] <- 8

FLUKE_edges <- cbind(FLUKE,FLUKE_Colors)
FLUKE_Colors <- FLUKE_Colors[order(FLUKE_Colors$Color,FLUKE_Colors$Focus),]
FLUKE_Colors <- matrix(FLUKE_Colors$Color,dimnames=list(FLUKE_Colors$Focus,"Color"))
FLUKE_edges <-  FLUKE_edges[order( FLUKE_edges$Color,FLUKE_edges$Focus),]

FLUKE_edges$Color <- NULL
FLUKE_edges$Focus <- NULL


FLUKE_edges <- data.matrix(FLUKE_edges)
Border_mat <- matrix(1,nrow=nrow(FLUKE_edges),ncol=ncol(FLUKE_edges))
rownames(Border_mat) <- rownames(FLUKE_edges)
colnames(Border_mat) <- colnames(FLUKE_edges)
#Border_mat[Grand_Banks_edges < 0] = 2
Border_Col <- matrix("white",nrow=nrow(FLUKE_edges),ncol=ncol(FLUKE_edges))
rownames(Border_Col) <- rownames(FLUKE_edges)
colnames(Border_Col) <- colnames(FLUKE_edges)
#Border_Col[Grand_Banks_edges < 0] = "black"

Border_w <- matrix(.0001,nrow=nrow(FLUKE_edges),ncol=ncol(FLUKE_edges))
rownames(Border_w) <- rownames(FLUKE_edges)
colnames(Border_w) <- colnames(FLUKE_edges)

```
<!--
## Static Plot

```{r sfstatic}
#full conceptual model in circlize package
chordDiagram(FLUKE_edges, directional=0,
                   grid.col = FLUKE_Colors,
                   row.col = FLUKE_Colors,
                   link.lty = Border_mat,
                   link.lwd = Border_w,
                   link.border = Border_Col,
                   annotationTrack="grid",preAllocateTracks= list(track.height=0.5))

circos.trackPlotRegion(track.index=1, panel.fun= function (x,y){
  xlim = get.cell.meta.data("xlim")
  ylim = get.cell.meta.data("ylim")
  sector.name = get.cell.meta.data("sector.index")
  circos.text(mean(xlim),ylim[1],sector.name,facing="clockwise", niceFacing=TRUE, adj =c(0,0.5), cex=.6)
}, bg.border=NA) 

legend(x=-1.1,y = 1.09,legend = c("Driver","Habitat","Fluke","Other Biota","Management","Benefits","Science","Fishing Fleets"),
             lty= c(1,1,1,1,1,1,1,1), lwd=c(5,5,5,5,5,5,5,5),
             col =c(FLUKE_C[1],FLUKE_C[2],FLUKE_C[3],FLUKE_C[4],FLUKE_C[5],FLUKE_C[6],FLUKE_C[7],FLUKE_C[8]), ncol=1, cex = .75, bg = NULL, box.col=NULL, bty = "n")
title(main="Fluke System", line=-35)


```
-->
## Interactive Plot: Risk Factors only

Limks from a model element start wide at the base and are color coded to match the category of the element they lead to. Hover over a perimeter section (an element) to see all relationships for that element, including links from other elements. Hover over a link to see what it connects.

```{r sfintsetup}

#need to redo the order of the columns and rows for this function
#also transpose it and no negative values
FLUKE_Colors <- data.frame(row.names(FLUKE))
colnames(FLUKE_Colors) <- "Focus"

FLUKE_Colors$Color <- FLUKE_C[1]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Habitat] <- FLUKE_C[2]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Biota] <- FLUKE_C[3]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Species] <- FLUKE_C[4]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Management] <- FLUKE_C[5]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Benefits] <- FLUKE_C[6]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Science] <- FLUKE_C[7]
FLUKE_Colors$Color[FLUKE_Colors$Focus%in%FLUKE_Fishery] <- FLUKE_C[8]

FLUKE_edges <- cbind(FLUKE,FLUKE_Colors)
FLUKE_Colors <- FLUKE_Colors[order(FLUKE_Colors$Color,FLUKE_Colors$Focus),]
FLUKE_Colors <- matrix(FLUKE_Colors$Color,dimnames=list(FLUKE_Colors$Focus,"Color"))
FLUKE_edges <-  FLUKE_edges[order( FLUKE_edges$Color,FLUKE_edges$Focus),]

FLUKE_edges$Color <- NULL
FLUKE_edges$Focus <- NULL

rn <- row.names(FLUKE_edges)
FLUKE_edges2 <- FLUKE_edges[rn]

FLUKE_edges <- data.matrix(FLUKE_edges)
FLUKE_edges2 <- data.matrix(FLUKE_edges2)
FLUKE_edges2 <- t(FLUKE_edges2)
FLUKE_edges2 <- abs(FLUKE_edges2)

 #########Submodels functions
Submodel_edges <- function (y) {
  New_edges <- FLUKE_edges2[,colnames(FLUKE_edges2)%in%y]
  New_edges <- New_edges[rownames(New_edges)%in%y,]
    return(New_edges)
}

Submodel_color <- function (y) {
  New_colors <-  as.vector(FLUKE_Colors[rownames(FLUKE_Colors)%in%y,])
  return(New_colors)
}

New_Figure <- function (x) {

New_edges <- Submodel_edges(x)
New_colors <- Submodel_color(x)
New_groups <- FLUKE_Groups[which(FLUKE_Groups$Focus%in%x),]
  New_groups <- unique(New_groups[,2:4])
  New_groups <- New_groups[order(New_groups$Rank),]
  New_groups <- New_groups[,1:2]
  Figure_name <- deparse(substitute(x))
  Figure_title <- gsub("_"," ",Figure_name)

chorddiag(New_edges, 
          type = "directional",
          width = 900,
          height = 900,
          margin = 120,
          groupColors = New_colors,
          groupedgeColor = New_colors,
          chordedgeColor = New_colors,
          groupPadding = 1, groupThickness = 0.1,
          showTicks = F, groupnameFontsize = 12, groupnamePadding = 10
          )
}
```

```{r sfint-risk}

#1. Risk Factors
Risk_Factors <- c('Allocation','Commercial Profits','Discards','Fishery Resilience','Fleet Diversity','Management Control',
                  'Recreational Value','Regulatory Complexity','Seafood','Technical Interactions',"Fluke Distributional Shift",
                  "Estuarine Habitat", "Fluke SSB","Stock Assessment","Offshore Habitat")
New_Figure(Risk_Factors)

```


## Documentation Tables

Each link in the conceptual model corresponds to an entry in the documentation tables below. Click on the category name to see the full documentation assembled by the working group.

```{r googledr, message=FALSE, eval=FALSE}
# take from google drive to automatically update any changes
drive_download("Conceptual Model Elements_Detailed Info Table", path="documentation.xlsx", overwrite = TRUE)

```

### Physical Environment {.tabset .tabset-fade}

#### Distribution Change
```{r distchange}
knitr::kable(read_excel("documentation.xlsx", sheet="Physical Environment", range = 'A3:E13')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Estuarine Habitat
```{r esthab}
knitr::kable(read_excel("documentation.xlsx", sheet="Physical Environment", range = 'A17:E28')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Fluke SSB (Stock Biomass)
```{r SSB}
knitr::kable(read_excel("documentation.xlsx", sheet="Physical Environment", range = 'A32:E44')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Stock Assessment
```{r stockassess}
knitr::kable(read_excel("documentation.xlsx", sheet="Physical Environment", range = 'A48:E52')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Offshore Habitat
```{r offhab}
knitr::kable(read_excel("documentation.xlsx", sheet="Physical Environment", range = 'A56:E64')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Human Dimensions {.tabset .tabset-fade}

#### Allocation
```{r alloc}
knitr::kable(read_excel("documentation.xlsx", sheet="Human Dimension", range = 'A3:E8')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Commercial Profits
```{r commprofit}
knitr::kable(read_excel("documentation.xlsx", sheet="Human Dimension", range = 'A12:E24')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Discards
```{r discards}
knitr::kable(read_excel("documentation.xlsx", sheet="Human Dimension", range = 'A28:E34')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Fishery Resilience (Shoreside Support)
```{r resilience}
knitr::kable(read_excel("documentation.xlsx", sheet="Human Dimension", range = 'A38:E43')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Fleet Diversity
```{r fldiversity}
knitr::kable(read_excel("documentation.xlsx", sheet="Human Dimension", range = 'A47:E52')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Management Control
```{r control}
knitr::kable(read_excel("documentation.xlsx", sheet="Human Dimension", range = 'A56:E864')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Recreational Value
```{r recval}
knitr::kable(read_excel("documentation.xlsx", sheet="Human Dimension", range = 'A68:E79')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Regulatory Complexity
```{r regcomplex}
knitr::kable(read_excel("documentation.xlsx", sheet="Human Dimension", range = 'A83:E89')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Seafood Production
```{r seafood}
knitr::kable(read_excel("documentation.xlsx", sheet="Human Dimension", range = 'A93:E100')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

#### Technical Interactions
```{r techint}
knitr::kable(read_excel("documentation.xlsx", sheet="Human Dimension", range = 'A104:E108')) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
